\documentclass[uplatex,dvipdfmx]{jsarticle}
\title{Curriculum Vitae}
\author{Hirofumi Shiba}
\date{\today}
\pagestyle{empty} \setcounter{secnumdepth}{4}
\input{/Users/Hirofumi Shiba/NatureOfStatistics/preamble_no_fonts.tex}
%\input{/Users/hirofumi.shiba48/NatureOfStatistics/preamble_no_fonts.tex}
%\input{/Users/hirof/NatureOfStatistics/preamble_no_fonts.tex}
\usepackage[math]{anttor}
\begin{document}
\maketitle

\begin{itemize}
    \item Date and place of birth: 05/30/1999, Yokohama, Japan
    \item Email: \href{mailto:hirofumi-shiba48@g.ecc.u-tokyo.ac.jp}{hirofumi-shiba48@g.ecc.u-tokyo.ac.jp}
    \item Home page: \url{https://anomath.com/about-us/hs/}
    \item Current Position: Ph.D. candidate at \href{https://www.ism.ac.jp/index_e.html}{the Institute of Statistical Mathematics}
    \item Research Interest: Causal Inference, Statistical Inference for Stochastic Processes, Malliavin Calcullus.
    \item Language: Japanese, English, Mandarine Chinese
\end{itemize}

\section*{Educatation}

\begin{itemize}
    \item Bachelor of Mathematics, University of Tokyo, 2022
\end{itemize}

\section*{Acticities}

\begin{itemize}
    \item Aug. 2022- Project Researcher at \href{http://imis.jp/}{IMIS}
    %\item Apr. 2022- Mar. 2023 Teaching Assistant at Univ. of Tokyo
    \item Dec. 2021- Mar. 2023 Research Assistant at Univ. of Tokyo under Prof. \href{https://www.ms.u-tokyo.ac.jp/~nakahiro/hp-naka-e}{Nakahiro Yoshida}
    \item May 2021- Nov. 2021 Research Assistant at Univ. of Saitama under Prof. \href{https://www.u-tokyo.ac.jp/focus/ja/people/k0001_01178.html}{Park Young Won}
    \item Feb. 2021- Mar. 2023 Research Assistant at \href{https://www.rcast.u-tokyo.ac.jp/en/}{RCAST} under Prof. \href{https://www.u-tokyo.ac.jp/focus/en/people/people002854.html}{Katsuya Tamai}
\end{itemize}

\end{document}